### 2021-09-03 presentation/presentation.tex
correct space
add context images

  % or whatever (possibly just delete it)
}

@@

\author[Nogueira, Bourdais, Guéguen] % (optional, use only with lots of authors)
{R. A. Nogueira \and  R. Bourdais \and  H. Guéguen\\
\texttt{\{rafael-accacio.nogueira, romain.bourdais, herve.gueguen\}\\ at \\ centralesupelec.fr}}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

@@

% \begin{frame}[fragile]
% \frametitle{An Algorithm For Finding Primes Numbers.}
% \begin{semiverbatim}
% \uncover<1->{\alert<0>{int main (void)}}
% \uncover<1->{\alert<0>{\{}}
% \uncover<1->{\alert<1>{ \alert<4>{std::}vector<bool> is_prime (100, true);}}
% \uncover<1->{\alert<1>{ for (int i = 2; i < 100; i++)}}
% \uncover<2->{\alert<2>{
% if (is_prime[i])}}
% \uncover<2->{\alert<0>{
% \{}}
% \uncover<3->{\alert<3>{
% \alert<4>{std::}cout << i << " ";}}
% \uncover<3->{\alert<3>{
% for (int j = i; j < 100;}}
% \uncover<3->{\alert<3>{
% is_prime [j] = false, j+=i);}}
% \uncover<2->{\alert<0>{
% \}}}
% \uncover<1->{\alert<0>{ return 0;}}
% \uncover<1->{\alert<0>{\}}}
% \end{semiverbatim}
% \visible<4->{Note the use of \alert{\texttt{std::}}.}
% \end{frame}

\begin{frame}
\SetKwBlock{negotPhase}{ Negotiation Phase:}{}
\SetKwBlock{detectPhase}{ Detection Phase:}{}
\scalebox{.8}{  \begin{algorithm}[H]
    \DontPrintSemicolon
    \detectPhase{
    $h:=0$\;
    \Repeat{
    $\|\eta_{i}^{h}-\eta^{h-1}\|\leq\epsilon$
  }{
    Coordinator sets random $\vec{\theta}_{i}^{(h+1)}$ \;
    Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}^{(h)})$\;
    Coordinator estimates $\widehat{\tilde{P}}_{i}(k)^{(h)}$ and $\widehat{\tilde{\vec{s}}}_{i}(k)^{(h)}$ \;
    $h:=h+1$\;
  }
    Coordinator computes $d_{i}$ using~\eqref{eq:2}\;
  }
    \negotPhase{
    Coordinator initializes $\vec{\theta}^{(0)}$ \;
    $p:=0$\;

    \Repeat{$\|\vec{\theta}^{(p)} -\vec{\theta}^{(p-1)}\|\leq\epsilon$}{
    Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}\p)$\;

    Coordinator updates allocation~\eqref{eq:thetaNegot} using adequate versions of $\vec{\lambda}_{i}$ for each agent: $\vec{\lambda}_{i}^{\star}(\vec{\theta}\p)$, if $d_{i}=0$ and ${\vec{\lambda}_{i}}_{\mathrm{rec}}$, if ${d_{i}=1}$\;
    $p:=p+1$
  }}
    \caption{Secure DMPC.}\label{alg:safeDMPC}
  \end{algorithm}
  }

\end{frame}

@@

      \draw[-latex] (block5) -| ($(block2.west) - (1.5cm,0)$)
      node[pos=0.25,fill=white,inner sep=0]{No} -- (block2.west);
    \end{tikzpicture}
    }
    \caption{Scheme of DMPC using a \emph{coordinator} and $M$ agents.}\label{fig:schemeQuantity}
  \end{figure}
\end{frame}

\begin{frame}
  \centering
  \begin{minipage}{.65\linewidth}
    \begin{algorithm}[H]
      \DontPrintSemicolon
      Coordinator initializes $\vec{\theta}^{(0)}$ \;
      $p:=0$\;
      \Repeat{$\|\vec{\theta}^{(p)} -\vec{\theta}^{(p-1)}\|\leq\epsilon$}{
        Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}\p)$\;
        Coordinator updates allocations~\eqref{eq:thetaNegot}\;
        $p:=p+1$
      }
      \caption{Quantity decomposition based DMPC.}\label{alg:quantityAlg}
    \end{algorithm}
  \end{minipage}
\end{frame}

\section{Motivation}

\begin{frame}{Make Titles Informative. Use Uppercase Letters.}{Subtitles are optional.}
  % - A title should summarize the slide in an understandable fashion
  %   for anyone how does not follow everything on the slide itself.

  \begin{itemize}
  \item
    Use \texttt{itemize} a lot.
  \item
    Use very short sentences or short phrases.
  \end{itemize}
\end{frame}

@@

\begin{frame}{Summary}
  \pause
  \begin{minipage}[t]{.45\textwidth}
    % Keep the summary *very short*.
    \begin{enumerate}
      \item
            Resource allocation based DMPC is vulnerable to attacks.
            \pause
      \item
            Sub-problems structure has time invariant parameters.
            \pause
      \item
            Attack can be estimated using these parameters.
            \pause
    \end{enumerate}
  \end{minipage}
  \pause
    % The following outlook is optional.
    % \vskip0pt plus.5fill
  \begin{minipage}[t]{.45\textwidth}
    \begin{itemize}
      \item Outlook
            \begin{itemize}
              \item
                    Inequality Constraints yield Hybrid behavior
              \item
                    Non-linear attack model
            \end{itemize}
    \end{itemize}
  \end{minipage}
\end{frame}

\nocite{VelardeEtAl2017a}
% All of the following is optional and typically not needed.
% \appendix
% \section<presentation>*{\appendixname}
% \subsection<presentation>*{For Further Reading}

\begin{frame}[allowframebreaks]
% \bibliographystyle{IEEEtran}
% \bibliography{../article/bibliography}
  \frametitle<presentation>{For Further Reading}

@@

  \bibitem{Someone2000}
    S.~Someone.
    \newblock On this and that.
    \newblock {\em Journal of This and That}, 2(1):50--100,
    2000.
  \end{thebibliography}
\end{frame}

\begin{frame}[plain]
  \centering
  \vfill
  Questions?
  \vfill
  \begin{minipage}[t]{.45\linewidth}
    \small
    \centering
    Repository
    \href{https://github.com/Accacio/SysTol-21}{https://github.com/Accacio/SysTol-21}

>>>>

\setbeamertemplate{caption}[numbered]
  % or whatever (possibly just delete it)
}

@@

\author[Nogueira, Bourdais, Guéguen] % (optional, use only with lots of authors)
{R. A. Nogueira \and  R. Bourdais \and  H. Guéguen\\
\texttt{\{rafael-accacio.nogueira, romain.bourdais, herve.gueguen\} at  centralesupelec.fr}}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

@@

\begin{frame}{Context}
  \begin{figure}
    \includegraphics<1>[width=.6\textwidth]{the_city_nothing.pdf}%
    \includegraphics<2>[width=.6\textwidth]{the_city_houses.pdf}%
    \includegraphics<3>[width=.6\textwidth]{the_city_buildings.pdf}%
    \includegraphics<4>[width=.6\textwidth]{the_city_cars.pdf}%
  \end{figure}
  \onslide<5->{
  \begin{minipage}{.45\textwidth}
    \includegraphics[width=\textwidth]{the_city_cars.pdf}%
  \end{minipage}
  \begin{minipage}{.5\textwidth}
    \begin{itemize}
      \item<6> Geographically distributed
      \item<7> Coupled by constraints (energy)
      \item<8> Optimization objectives
            \begin{itemize}
              \item Energy
              \item User satisfaction
              \item \dots
            \end{itemize}
      \item<9> Solution $\to$ Model Predictive Control
    \end{itemize}
  \end{minipage}
  }
\end{frame}

\begin{frame}{Model Predictive Control}
  Find control input sequence that optimizes an objective function

\begin{equation*}
\begin{matrix}
\underset{\vec{u}(k:k+N_{p}-1|k)}{\mathrm{minimize}}&\resizebox{0.35\textwidth}{!}{$ \overbrace{\sum_{j=1}^{N_{p}}\|\vec{v}(k+j|k)\|^{2}_{Q}+\|\vec{u}(k+j-1|k)\|^{2}_{R}}^{\textstyle J_{G}(k)}$}\\
\mathrm{subject~ to}&
\left.\begin{matrix}
    \vec{x}(k+1)=f(\vec{x}(k),\vec{u}(k)) \\
    g_{i}(\vec{x}(k),\vec{u}(k))=0\\
    h_{k}(\vec{x}(k),\vec{u}(k))\leq0\\
\end{matrix}
\right\}
\begin{aligned}
  &\forall i\in\{1,\dots,N_{p}\}\\
  &\forall j\in\{1,\dots,N_{p}\}\\
  &\forall k\in\{1,\dots,N_{p}\}
\end{aligned}
\end{matrix}
\end{equation*}
  Using
\end{frame}

% \begin{frame}
%   \centering
%   \begin{minipage}{.65\linewidth}
%     \begin{algorithm}[H]
%       \DontPrintSemicolon
%       Coordinator initializes $\vec{\theta}^{(0)}$ \;
%       $p:=0$\;
%       \Repeat{$\|\vec{\theta}^{(p)} -\vec{\theta}^{(p-1)}\|\leq\epsilon$}{
%         Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}\p)$\;
%         Coordinator updates allocations~\eqref{eq:thetaNegot}\;
%         $p:=p+1$
%       }
%       \caption{Quantity decomposition based DMPC.}\label{alg:quantityAlg}
%     \end{algorithm}
%   \end{minipage}
% \end{frame}

\begin{frame}
  \begin{figure}
    \centering
    \scalebox{.6}{
      \begin{tikzpicture}[font=\small,thick,node distance=.6cm and 6cm]
        \node[draw,
        rounded rectangle,
        fill=gray!90!black!50,
        alt=<{2}>{fill=supelecRed!90,text=white},
        minimum width=2.5cm,
        minimum height=1cm] (block1) {Start};

        \node[draw,
        trapezium,
        trapezium left angle = 65,
        trapezium right angle = 115,
        trapezium stretches,
        align=center,
        below=of block1,
        fill=supelecRed!10,
        alt=<{3}>{fill=supelecRed!90,text=white},
        minimum width=3.5cm,
        minimum height=1cm
        ] (block7) { Coordinator sends \\$\vec{\theta}_i^{(h)}$};
        \node[draw,
        trapezium,
        trapezium left angle = 65,
        trapezium right angle = 115,
        trapezium stretches,
        align=center,
        fill=supelecRed!10,
        alt=<{4}>{fill=supelecRed!90,text=white},
        below=of block7,
        minimum width=3.5cm,
        minimum height=1cm
        ] (block8) { Agents send \\$\vec{\lambda}_i(\vec{\theta}_{i}^{(h)})$};

        \node[draw,
        trapezium,
        trapezium left angle = 65,
        trapezium right angle = 115,
        trapezium stretches,
        align=center,
        fill=supelecRed!10,
        alt=<{5}>{fill=supelecRed!90,text=white},
        below=of block8,
        minimum width=3.5cm,
        minimum height=1cm
        ] (block9) { Coordinator updates \\allocation};

        \node[draw,
        diamond,
        below=of block9,
        minimum width=2.5cm,
        fill=supelecRed!50,
        alt=<{6}>{fill=supelecRed!90,text=white},
        align=center,
        inner sep=0] (block10) { Negotiation\\ converges?};

        \node[draw,
        rounded rectangle,
        below=of block10,
        fill=gray!90!black!50,
        alt=<{7}>{fill=supelecRed!90,text=white},
        minimum width=2.5cm,
        minimum height=1cm,] (block11) { Apply first control};

        \draw[-latex] (block7) edge (block8)
        (block1) edge (block7)
        (block8) edge (block9)
        (block9) edge (block10);

      \end{tikzpicture}
    }
    \caption{Quantity decomposition based DMPC}\label{fig:quantityDecompDMPC}
  \end{figure}
\end{frame}

\section[Vulnerabilities in DMPC based on Resource Allocation]{Vulnerabilities in distributed MPC based on Resource Allocation}

\begin{frame}{Make Titles Informative. Use Uppercase Letters.}{Subtitles are optional.}
  \begin{itemize}
  \item
    Use \texttt{itemize} a lot.
  \item
    Use very short sentences or short phrases.
  \end{itemize}
\end{frame}

\section{Securing the DMPC}
% \begin{frame}
% \SetKwBlock{negotPhase}{ Negotiation Phase:}{}
% \SetKwBlock{detectPhase}{ Detection Phase:}{}
% \scalebox{.8}{  \begin{algorithm}[H]
%     \DontPrintSemicolon
%     \detectPhase{
%     $h:=0$\;
%     \Repeat{
%     $\|\eta_{i}^{h}-\eta^{h-1}\|\leq\epsilon$
%   }{
%     Coordinator sets random $\vec{\theta}_{i}^{(h+1)}$ \;
%     Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}^{(h)})$\;
%     Coordinator estimates $\widehat{\tilde{P}}_{i}(k)^{(h)}$ and $\widehat{\tilde{\vec{s}}}_{i}(k)^{(h)}$ \;
%     $h:=h+1$\;
%   }
%     Coordinator computes $d_{i}$ using~\eqref{eq:2}\;
%   }
%     \negotPhase{
%     Coordinator initializes $\vec{\theta}^{(0)}$ \;
%     $p:=0$\;

%     \Repeat{$\|\vec{\theta}^{(p)} -\vec{\theta}^{(p-1)}\|\leq\epsilon$}{
%     Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}\p)$\;

%     Coordinator updates allocation~\eqref{eq:thetaNegot} using adequate versions of $\vec{\lambda}_{i}$ for each agent: $\vec{\lambda}_{i}^{\star}(\vec{\theta}\p)$, if $d_{i}=0$ and ${\vec{\lambda}_{i}}_{\mathrm{rec}}$, if ${d_{i}=1}$\;
%     $p:=p+1$
%   }}
%     \caption{Secure DMPC.}\label{alg:safeDMPC}
%   \end{algorithm}
%   }
% \end{frame}

@@

      \draw[-latex] (block5) -| ($(block2.west) - (1.5cm,0)$)
      node[pos=0.25,fill=white,inner sep=0]{No} -- (block2.west);
    \end{tikzpicture}
    }
    \caption{Secure DMPC}\label{fig:secureDMPC}
  \end{figure}
\end{frame}

@@

\begin{frame}{Summary}
  \pause
  \begin{minipage}[t]{.45\textwidth}
    % Keep the summary *very short*.
    \begin{enumerate}
      \item
            Resource allocation based DMPC is vulnerable to attacks.
            \pause
      \item
            Sub-problems structure has time invariant parameters.
            \pause
      \item
            Attacks can be detected using these parameters.
    \end{enumerate}
  \end{minipage}
  \pause
    % The following outlook is optional.
    % \vskip0pt plus.5fill
  \begin{minipage}[t]{.45\textwidth}
    \begin{itemize}
      \item Outlook
            \pause
            \begin{itemize}
              \item
                    Inequality Constraints yield Hybrid behavior
                    \pause
              \item
                    Non-linear attack model
            \end{itemize}
    \end{itemize}
  \end{minipage}
\end{frame}

% \nocite{VelardeEtAl2017a}
% All of the following is optional and typically not needed.
% \appendix
% \section<presentation>*{\appendixname}
% \subsection<presentation>*{For Further Reading}

\appendix
\begin{frame}[allowframebreaks]
% \bibliographystyle{IEEEtran}
% \bibliography{../article/bibliography}
  \frametitle<presentation>{For Further Reading}

@@

  \bibitem{Someone2000}
    S.~Someone.
    \newblock On this and that.
    \newblock {\em Journal of This and That}, 2(1):50--100,
    2000.
  \end{thebibliography}
\end{frame}
\begin{frame}[plain]
  \centering
  \vfill
  Questions?
  \vfill
  \begin{minipage}[t]{.45\linewidth}
    \small
    \centering
    Repository
    \href{https://github.com/Accacio/SysTol-21}{https://github.com/Accacio/SysTol-21}
